Central Slot Value Extraction from Internet for Wikipedia Entities

### 2013-11-03 paper/flairs27/content/conclusion.tex
added the paper for FLAIRS27. It needs a LOT of work
remove extra newlines instead of wrap
New review, check image

\section{Conclusions}

We experimented through different tools and approaches to best process the massive amounts of data on the platform that we had available to us. We generate aliases for wikipedia entities using Wiki API and extract some aliases from wikipedia pages text itself. On twitter entities we extract aliases manually as it is part of the rule of the KBA track. We process   documents that mention entities for slot value extraction. Slot values are determined using pattern matching over coreferences of entities in sentences. Finally post processing will filter, cleanup and infers some new slot values to enhance recall and accuracy.

We noticed that some tools that claim to be performant for using the hardware capabilities at hand sometimes don't really work as claimed and you should not always rely on one without a thorough A/B testing of performance which we ended up in generating our in-house system for processing the corpus and generating the index. Furthermore, on extracting slot values, pattern matching might not be the best options but definitely can produce some good results at hand. We have plans on generating classifiers for slot value extraction purposes. Entity resolution on the other hand was a topic we spent sometime on but could not get to stable grounds for it. Entity resolution will distinguish between entities of the same name but different contexts. Further improvements on this component of the system are required.

>>>>

%\section{Conclusions}

### 2013-11-03 paper/flairs27/content/introduction.tex
New review, check image

 An important challenge in maintaining Wikipedia.org (WP), the most popular web-based, collaborative, multilingual knowledge base on the internet, is making sure its contents are up-to-date. Presently, there is considerable time lag between the publication date of cited news and the date of an edit to WP creating the citation. The median time lag for a sample of about 60K web pages cited by WP articles in the \textit{living\_people} category is over a year and the distribution has a long and heavy tail \cite{JFrank12}. Also, the majority of WP entities have updates on their associated article much less frequently than their mention frequency. Such stale entries are the norm in any large knowledge base (KB) because the number of humans maintaining the KB is far fewer than the number of entities. %Further, the number of mentions is much larger than the number of entities~\cite{JFrank12}. 
Reducing latency keeps KBs such as WP relevant and helpful it users.

Given an entity page, possible citations may come from a variety of sources. The actual citable information is a small percentage of the total documents that appear on the web. We develop a system to read streaming data and filter out articles that are candidates for citations. Given these documents, we extract the pairs of information in the article that is recommended for citations for each entity page in  WP. Some of the challenges that we face in this regard includes: having to balance between infamous and obscure enitities, ambiguous entities (entities of exact same name that are differnet in real life), facts that can very broad e.g. things that an entity is affiliated with or very specific such as cause of death of a \textit{person} entity.

>>>>

 An important challenge in maintaining Wikipedia.org (WP), the most popular web-based, collaborative, multilingual knowledge base on the internet, is making sure its contents are up-to-date. Presently, there is considerable time lag between the publication date of cited news and the date of an edit to WP creating the citation. The median time lag for a sample of about 60K web pages cited by WP articles in the \textit{living\_people} category is over a year and the distribution has a long and heavy tail \cite{JFrank12}. Also, the majority of WP entities have updates on their associated article much less frequently than their mention frequency. Such stale entries are the norm in any large knowledge base (KB) because the number of humans maintaining the KB is far fewer than the number of entities. %Further, the number of mentions is much larger than the number of entities~\cite{JFrank12}. 
Reducing latency keeps KBs such as WP relevant and helpful to it users.

Given an entity page, possible citations may come from a variety of sources. The actual citable information is a small percentage of the total documents that appear on the web. We develop a system to read streaming data and filter out articles that are candidates for citations. Given these documents, we extract the pairs of information in the article that is recommended for citations for each entity page in  WP. Some of the challenges that we face in this regard includes: having to balance between infamous and obscure enitities, ambiguous entities (entities of exact same name that are differnet in real life), facts that can very broad (e.g. things that an entity is affiliated with) or very specific (such as cause of death of a \textit{person} entity).

### 2013-11-03 paper/flairs27/content/results.tex
remove extra newlines instead of wrap
New review, check image

\section{Results}
\label{sec:results}

%\ceg{We can add data on the total document size, The %number of each document type.  } 
 Our system was developed on a 32-core server described in
 Table~\ref{table:serverspec}. The corpus is a snapshot of the web in English.
 Each document is annotated using lingpipe and is called StreamItem, a bundle of 
StreamItems are put together and serialized as Apache Thrift objects, then 
compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) 
and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys.
The total size of the data after XZ compression and GPG encryption is 4.5TB and
just over 500M StreamItems \cite{s3}. Data is stored in directories the naming
of which is date-hour combination: from 2011-10-05-00 (5th of October 2011, 12am)
until 2013-02-13-23 (13th of Feburary 2013, 11pm), which consists of 11952
date-hour combinations. This corpora consists of various media types the
distribution of which can be found in Table~\ref{table:documentsDist}. To have a
sense of the scale of objects and compression as an example a 6mb
gpg.xz files would become 45 mb thrift objects which can contain a couple of 
thousand StreamItems depending on their size. Some of the documents have null 
values for their annotation fields. The first portion of the data which 
ranges from October 2011 to February 2012 is considered as training data.
The source code of our system is stored as an open source project where
enthusiasts can also contribute to \cite{github}, also the relevant discussion
mailing list is accessible here \cite{googlegroups}.

>>>>

\section{Evaluation}
\label{sec:results}

%\ceg{We can add data on the total document size, The %number of each document type.  } 
 Our system was developed on a 32-core server described in Table~\ref{table:serverspec}. The corpus is a snapshot of the web in English. Each document is annotated using lingpipe and is called StreamItem, a bundle of StreamItems are put together and serialized as Apache Thrift objects, then compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys. The total size of the data after XZ compression and GPG encryption is 4.5TB and just over 500M StreamItems \cite{s3}. Data is stored in directories the naming of which is date-hour combination: from 2011-10-05-00 (5th of October 2011, 12am) until 2013-02-13-23 (13th of Feburary 2013, 11pm), which consists of 11952 date-hour combinations, 4 months of data (October 2011 - February 2012) is for training purposes. This corpora consists of various media types the distribution of which can be found in Table~\ref{table:documentsDist}. To have a sense of the scale of objects and compression as an example a 6mb gpg.xz files would become 45 mb thrift objects which can contain a couple of thousand StreamItems depending on their size. Some of the documents have null values for their annotation fields. The first portion of the data which ranges from October 2011 to February 2012 is considered as training data. The source code of our system is stored as an open source project where enthusiasts can also contribute to \cite{github}, also the relevant discussion mailing list is accessible here \cite{googlegroups}.

### 2013-11-03 paper/flairs27/content/system.tex
Updating paper independent of trek kba terminology
remove extra newlines instead of wrap
New review, check image

In this section, we introduce the main components of the system. Our system is 
built with a pipeline architecture in mind giving it the advantage to run 
each section separately to allow stream processing without blocking the data flow of components 
(Figure~\ref{fig:system}).
The three logical components include sections for performing preprocessing to prepare the required data, 
Cumulative Citation Recommendation to annotate cite-worthy documents, Streaming 
Slot Filling to generate the actual slot values and PostProcessing to 
increase precision/recall. 
TREC provides a streaming data set and  entities from Twitter or WP to query.

@@

\begin{figure}
  \centering
%\includegraphics[width=6in]{./images/sdl.eps}
  \includegraphics[width=6in]{./images/sdl-eps-converted-to.pdf}
% http://convert.neevia.com/pdfconvert/
  \vspace*{-.1in} 
  \caption{The GatorDSR team System Architecture.
  Components are logically groups with dotted boxes.
  Color details the programing language implementation of components.}
  \label{fig:system}
  \vspace*{-.2in}
\end{figure}

\textbf{Preprocessing.}
\label{sec:preproc}
The contest prohibits Wikipedia entities to have any manual aliases being added and only
allows automatic ways. We use Wikipedia API backlink references
(redirects to a wiki entity) as aliases of the entity. We also extract 
aliases from within the text of a wiki entity, which will be described in
Section~\ref{section:aliasgeneration}. This whole process is referred to as
\textit{Alias Extraction}. 
The manual extraction rule is lifted and participants are allowed to manually add aliases for Twitter entities.
This is allowed because the Twitter website does not provide an example page from the beginning of the document stream.
This process of extracting
aliases for Twitter entities is referred to as \textit{Manual Alias Extraction}.

@@

\textbf{Cumulative Citation Recommendation.}
\label{sec:ccr1}
The main goal of CCR is to have an aggregate list of documents that are worthy of being cited in a Wikipedia page. We perform exact string matching 
and treat all the documents that mention an entity equally likely to be citable. One of the reasons for this is 
that in former TREC KBA reports \cite{JFrank12} there were observations of how 
non-mentioning documents have a low chance of being citable in Wikipedia.
So we take on that and ignore non-citing documents.

@@

\textbf{Streaming Slot Filling.}
\label{sec:ssf1}
%\ceg{See the previous note.}
The purpose of SSF is to extract proper values for relations of
interest, which can be found in Table~\ref{table:slotNameOntology}.
This is called Stream Slot Filling because data is being generated as time goes
on and for each extraction we should only consider current or past data.
In Figure~\ref{fig:system} we refer to this as \textit{Streaming Slot Value Extraction}.
Stream slot filling is done by pattern matching documents with manually 
produced patterns for slots of interest. The way we do this is by observing a 
sentence that has a mention of the entity or one of its coreferences. An 
anchor word in the sentence related to the slot name is located and we match 
either left or right of the anchor word for potential slot values.

\textbf{Post Processing Algorithm.}
\label{sec:postproc}
The SSF output of many extractions is noisy. The data contains duplicates and 
incorrect extractions. We can define rules to sanitize the output only using 
the information present in the SSF file. The file is processed in time order, 
in a tuple-at-a-time fashion to minimize the impact on accuracy. We define 
two classes of rules deduplication rules and inference rules. In our diagram we refer to this component as \textbf{High Accuracy Filter}.

>>>>

In this section, we introduce the main components of the system. Our system is built with a pipeline architecture in mind giving it the advantage to run each section separately to allow stream processing without blocking the data flow of components (Figure~\ref{fig:system}). The three logical components include sections for performing preprocessing to prepare the required data, Cumulative Citation Recommendation to annotate cite-worthy documents, Streaming Slot Filling to generate the actual slot values and PostProcessing to increase precision/recall. We work on a streaming data set and entities are from Twitter or WP to query.

To walk you through the steps we take, assume we only care about on single WP entity, the first step is to extract aliases of the entity. We use several approaches to get as many viable aliases as possible. Then we look into the stream of content that is being generated on the internet, apply two levels of filtering to finally end up with the documents are central to that entity. To extract the relevnat slot values we perform pattern matching in each sentence or coreferent sentence to see if we can find a match. As a match is found from the content of the sentence to the patterns that we have generated regarding slot name, the associated slot value is extracted as a final result.

As mentioned before the time lag from an event occurance until it is cited in WP is in average over a year due to the fact that human maintainers are much less than the number of entities in WP and that the frequency of news update on entities escalates this difference. Hence having an automatic way to extract this knowldge for entities can be a very valuable asset.

@@

\begin{figure*}
  \centering
%  \includegraphics[width=6in]{./images/sdl-eps-converted-to.pdf}
  \includegraphics[width=6in]{./images/System_Diagram_with_model_Vertical.pdf}
% http://convert.neevia.com/pdfconvert/
  \vspace*{-.1in} 
  \caption{The GatorDSR team System Architecture.
  Components are logically groups with dotted boxes.
  Color details the programing language implementation of components.}
  \label{fig:system}
  \vspace*{-.2in}
\end{figure*}

\textit{Preprocessing.}
The contest prohibits Wikipedia entities to have any manual aliases being added and only allows automatic ways. We use Wikipedia API backlink references (redirects to a wiki entity) as aliases of the entity. We also extract aliases from within the text of a wiki entity, which will be described in Section~\ref{section:aliasgeneration}. This whole process is referred to as \textit{Alias Extraction}. The manual extraction rule is lifted and participants are allowed to manually add aliases for Twitter entities. This is allowed because the Twitter website does not provide an example page from the beginning of the document stream. This process of extracting aliases for Twitter entities is referred to as \textit{Manual Alias Extraction}.

@@

\textit{Cumulative Citation Recommendation.}
The main goal of CCR is to have an aggregate list of documents that are worthy of being cited in a Wikipedia page. We perform exact string matching and treat all the documents that mention an entity equally likely to be citable. One of the reasons for this is that in former TREC KBA reports \cite{JFrank12} there were observations of how non-mentioning documents have a low chance of being citable in Wikipedia. So we take on that and ignore non-citing documents.

@@

\textit{Streaming Slot Filling.}
%\ceg{See the previous note.}
The purpose of SSF is to extract proper values for relations of interest, which can be found in Table~\ref{table:slotNameOntology}. This is called Stream Slot Filling because data is being generated as time goes
on and for each extraction we should only consider current or past data. In Figure~\ref{fig:system} we refer to this as \textit{Streaming Slot Value Extraction}. Stream slot filling is done by pattern matching documents with manually produced patterns for slots of interest. The way we do this is by observing a sentence that has a mention of the entity or one of its coreferences. An anchor word in the sentence related to the slot name is located and we match either left or right of the anchor word for potential slot values.

\textit{Post Processing Algorithm.}
The SSF output of many extractions is noisy. The data contains duplicates and incorrect extractions. We can define rules to sanitize the output only using the information present in the SSF file. The file is processed in time order, in a tuple-at-a-time fashion to minimize the impact on accuracy. We define two classes of rules deduplication rules and inference rules. In our diagram we refer to this component as \textbf{High Accuracy Filter}.
